```{r}
library(tidyverse)
HAPPY <- readRDS("data/HAPPY.rds")
HAPPY
```

Data cleaning: the values “IAP”, “DK” and “NA” all encode missing values. Replace all of these instances by the value NA.

```{r}
HAPPY<-na_if(HAPPY,"IAP")
HAPPY<-na_if(HAPPY,"DK")
HAPPY<-na_if(HAPPY,"NA")
```

Check the type of the variable and cast into the right type (factor variable for categorical variables). For age, change “89 OR OLDER” to 89 and assume the variable should be numeric.
```{r}
str(HAPPY)
```
```{r}
HAPPY$HAPPY<-factor(HAPPY$HAPPY)
HAPPY$SEX<-factor(HAPPY$SEX)
HAPPY$MARITAL<-factor(HAPPY$MARITAL)
HAPPY$DEGREE<-factor(HAPPY$DEGREE)
HAPPY$FINRELA<-factor(HAPPY$FINRELA)
HAPPY$HEALTH<-factor(HAPPY$HEALTH)
HAPPY$PARTYID<-factor(HAPPY$PARTYID)
HAPPY$POLVIEWS<-factor(HAPPY$POLVIEWS)
HAPPY$AGE<-as.numeric(HAPPY$AGE)
levels(HAPPY$HAPPY)
levels(HAPPY$SEX)
levels(reorder(HAPPY$MARITAL, HAPPY$AGE, na.rm=TRUE))
levels(factor(HAPPY$DEGREE, 
              levels=c("LT HIGH SCHOOL", "HIGH SCHOOL", 
                     "JUNIOR COLLEGE", "BACHELOR", 
                     "GRADUATE")
              )
       )
levels(factor(HAPPY$FINRELA, 
              levels=c("FAR BELOW AVERAGE", "BELOW AVERAGE", 
                     "AVERAGE", "ABOVE AVERAGE", 
                     "FAR ABOVE AVERAGE")
              )
       )
levels(factor(HAPPY$HEALTH, 
              levels=c("POOR", "FAIR", 
                     "GOOD", "EXCELLENT")
              )
       )
levels(factor(HAPPY$PARTYID, 
              levels=c("STRONG DEMOCRAT", "NOT STR DEMOCRAT", "IND,NEAR DEM","INDEPENDENT",
                     "IND,NEAR REP", "NOT STR REPUBLICAN","STRONG REPUBLICAN",
                     "OTHER PARTY")
              )
       )
levels(factor(HAPPY$POLVIEWS, 
              levels=c("EXTREMELY LIBERAL", "LIBERAL", "SLIGHTLY LIBERAL","MODERATE",
                     "SLIGHTLY CONSERVATIVE", "CONSERVATIVE","EXTREMLY CONSERVATIVE")
              )
       )
saveRDS
```
```{r}
ggplot(HAPPY, aes(x = HAPPY)) + 
  geom_bar(na.rm=TRUE)
```

Pretty happy is the most common choice according to this chart.  

```{r}
ggplot(HAPPY, aes(x = AGE)) + 
  geom_bar(na.rm=TRUE)
```

It seems that the age chart is right skewed and most people that took the survey is about 29 years old.  

```{r}
ggplot(HAPPY, aes(x = MARITAL)) + 
  geom_bar(na.rm=TRUE)
```

Most people that answered the survey are married.  

```{r}
ggplot(HAPPY, aes(x = DEGREE)) + 
  geom_bar(na.rm=TRUE)
```

Most people that answered the survey are in high school.  

```{r}
ggplot(HAPPY, aes(x = FINRELA)) + 
  geom_bar(na.rm=TRUE) + theme(text=element_text(size=8))
```

The most common family income in the US seems to be average.  

```{r}
ggplot(HAPPY, aes(x = HEALTH)) + 
  geom_bar(na.rm=TRUE)
```

The most people that answered this survey seems to be in good health.  

```{r}
ggplot(HAPPY, aes(x = PARTYID)) + 
  geom_bar(na.rm=TRUE) +theme(text=element_text(size=6))
```

The most people that answered this survey are not strong democrat.  

```{r}
ggplot(HAPPY, aes(x = POLVIEWS)) + 
  geom_bar(na.rm=TRUE) +theme(text=element_text(size=6))
```

The most people that answered this survey has a moderate political view.  


Question from On Wave Tiong:  
How it the health of male or female in the US.  
```{r}
library(ggmosaic)
ggplot(data = HAPPY)  + 
  geom_mosaic(aes(x = product(SEX), fill=HAPPY, weight=1)) +
  facet_grid(.~HEALTH) +theme(text=element_text(size=5))
```

We can obviously see that people are not too happy when their health is poor and it seems like male and female have the same opinion. While in excellent health, male seems to be more happier than female. However, while in fair health, female seems to be more happier compare to male.

Question for Scott Madland:  
